The \textit{Kepler} Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-12-20 paper/ms.tex
huber radii

The spectroscopic properties are the effective temperature \teff, the metallicity \feh, and the surface gravities \logg from Table~\ref{stellar_props}. These are accompanied by the global asteroseismic properties \Dnu and \numax from Table~\ref{astero_table}. Theoretical predictions of \Dnu and \numax were computed using the asteroseismic scaling relation for any point along an evolutionary track or isochrone. For the solar values, we adopted $\nu_{\text{max, }\odot}=3090$~$\mu$Hz, $\Delta\nu_{\odot}=135.1$~$\mu$Hz \citep{huber2011}, and $T_{\text{eff, }\odot}=5777$~K.

@@

To gauge the level of improvement in our understanding of these stars, in Figure~\ref{gaia_comparison} we plot the radii determined here against those from the \gaia~DR2 catalog determined by the stellar bolometric flux and parallax. While not all of our targets have \gaia radii, we find that while there is overall agreement to within a few $\sigma$, the results from stellar modelling are consistently slightly larger than those from \gaia. One star noticeably very different: BD+39~3577 has a precise \gaia radius of $9.14^{+0.25}_{-0.13}$~\rsun, but $24.78^{+0.88}_{-0.72}$~\rsun from modelling. 
% Likewise BD+42~3150 has a \gaia radius of $15.70^{+0.52}_{-0.76}$~\rsun but $11.27^{+0.39}_{-0.41}$~\rsun from stellar modelling.
It is unclear why this would be the case; it is possible that an unidentified binary companion has affected either the asteroseismic detection or parallax.

@@

\begin{figure}
\noindent\includegraphics[width=8.5cm,keepaspectratio]{gaia_comparison.eps}

\caption{\label{gaia_comparison}
A comparison of the stellar radii determined here from asteroseismology and spectroscopy to those from the \gaia~DR2 catalogue. The catalogues disagree in most cases very significantly.}
\end{figure}

>>>>

The spectroscopic properties are the effective temperature \teff, the metallicity \feh, and the surface gravities \logg from Table~\ref{stellar_props}. These are accompanied by the global asteroseismic properties \Dnu and \numax from Table~\ref{astero_table}. Theoretical predictions of \Dnu and \numax were computed using the asteroseismic scaling relation for any point along an evolutionary track or isochrone. For the solar values, we adopted $\nu_{\text{max, }\odot}=3090$~$\mu$Hz, $\Delta\nu_{\odot}=135.1$~$\mu$Hz \citep{huber2011}, and $T_{\text{eff, }\odot}=5777$~K.
\newpage

@@

To gauge the level of improvement in our understanding of these stars, in Figure~\ref{gaia_comparison} we plot the radii determined here against those from the \gaia~DR2 catalog determined by the stellar bolometric flux and parallax.  We also calculate \gaia-like stellar bolometric radii using \texttt{isoclassify} \citep{huber2017} using our new spectroscopic \teff measurements rather than those from \gaia~DR2, together with \gaia~DR2 parallaxes spectroscopic \logg, $Z$, and SIMBAD $V$. While not all of our targets have \gaia radii, we find that while there is overall agreement to within a few $\sigma$, the results from stellar modelling are consistently slightly larger than those from \gaia. This discrepancy goes away for most stars when we use our own \texttt{isoclassify} radii, suggesting that this is an effect of \teff calibration. Two stars are noticeably very different: BD+39~3577 has a precise \gaia radius of $9.14^{+0.25}_{-0.13}$~\rsun, but $24.78^{+0.88}_{-0.72}$~\rsun from modelling. It is unclear why this would be the case; it is possible that an unidentified binary companion has affected either the asteroseismic detection or parallax. Likewise BD+42~3150 has a \gaia radius of $15.70^{+0.52}_{-0.76}$~\rsun but $11.27^{+0.39}_{-0.41}$~\rsun from stellar modelling, but of our sample it has the lowest \gaia parallax over error at only 18.0, and this anomalously high value is likely noise. Agreement for large-radius ($>30 \rsun$) stars is poorer, even though the \gaia parallax-over-error is apparently adequate. This disagreement, unlike for medium radius stars, is pronounced mainly for the \texttt{isoclassify} radii rather than \gaia~DR2, suggesting that our $V$ band bolometric corrections for these more yellow (\gaia $Bp-Rp \sim 0.25$) stars are insufficiently accurate.

@@

\begin{figure}
\noindent\includegraphics[width=8.5cm,keepaspectratio]{combined_radii.eps}

\caption{\label{gaia_comparison}
A comparison of the stellar radii determined here from asteroseismology and spectroscopy to those from the \gaia~DR2 catalogue and from our own calculations based on \gaia parallaxes and TRES spectroscopy. There is overall good agreement except for very large radii, except for BD+39~3577 (marked), which we do not understand.}
\end{figure}
